---
title: "In class assignment"
author: "Michael Roy"
date: "October 20, 2015"
output: html_document
---

##Question 1: Print each value of this matrix

####The following is false, and was an attempt for me to work out the problem:

```{r}
mat <- matrix(100:200, nrow = 10, ncol = 10)
mat
for(i in 1:100) {
  mat <- i
  print(mat)
}
```

####This is the correct answer, below:

```{r}
mat <- matrix(100:200, nrow = 10, ncol = 10)
print(mat)
for (c in 1:10) {
  for (r in 1:10)
    num<-mat[r, c]
    print(num)
}
```

##Question 2


##Question 3a: Print these values as part of a string that looks something like 'n = 16'.  Try to describe in words how creating the vector of numbers that you are going to use

####This is the correct answer below:

```{r}
set.seed(1)
x <- round(runif(min = 10, max = 100, n = 15))
for (i in 1:15) {
  numn <- x[i]
  numprint <- paste("n = ", numn)
  print(numprint)
}
```

####The following was what Lucy taught me about visualizing my loops:

```{r}
set.seed(1)
x <- round(runif(min = 10, max = 100, n = 15))
  print(x)
  for (i in 1:15) {
    print(i)
    numn <- x[i]
    print(numn)
    numprint <- paste("n =", numn)
    print(numprint)
  }
```

###Personal Notes
####NOTE:
####[Square Brackets are used for indexing]
####(paratheses are used for functions and order of operations)
####For Loops Takes the element of that vector at each step
  
####More tips from Lucy about elements within your index, and picking out a particular subset from your data (so you don't see thousands of data points if your data is that large)
  
```{r}  
  set.seed(1)
  x <- round(runif(min = 10, max = 100, n = 15))
  print(x[1:5])
  for (i in 1:15) {
    print(i)
    numn <- x[i]
    print(numn)
    numprint <- paste("n =", numn)
    print(numprint)
  }
```
