---
title: "Homework 2"
author: "Michael Roy"
date: "September 29, 2015"
output: html_document
---

I've included a header so that when you render the Rmarkdown document in RStudio
 it knows what kind of document to create, and includes some extra information 
 about the document.  


####Part I####
####Question 1####

```{r}
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, colour = continent, shape = continent)) + 
  geom_point()
```

####Question 2####

```{r}
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, colour = continent, shape = continent)) + 
  geom_point() +
  scale_x_log10() +
  #dev.new()
# You might not want to call dev.new() in the final rmarkdown (I'm not sure if 
# it tries to open )
```

####Question 3####
```{r}
y <- "lifeExp"
x <- "gdpPercap"

m <- lm(gdpPercap ~ lifeExp, data = gapminder)

ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, colour = continent)) + 
  geom_point() +
  scale_x_log10() +
  lm(gdpPercap ~ lifeExp, data = gapminder)
  
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + 
  geom_point() +
  scale_x_log10() +
  geom_quantile(lifeExp ~ gdpPercap)

ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + 
  geom_point() +
  scale_x_log10() +
  stat_smooth()

# JD: So close here! You just need to select the 'method' that the smoothing 
# statistic should be applied. 
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + 
  geom_point(aes(colour = continent, shape = continent)) + 
  scale_x_log10() +
  stat_smooth(method = 'lm')
```
  
####Question 4####
##### My notes: What am I coding?
##### density of Life expectancy for each continent every five years from 1952 to 2007

```{r}
ggplot(data = gapminder, aes(x = lifeExp, fill = continent)) + 
  geom_density(alpha = 0.5) +
  facet_wrap(~ year) 
```

####Part II####
####Question 6####
```{r}
ggplot(data = gapminder, aes(x = lifeExp, by = continent, fill = continent)) +
  geom_density(alpha = 0.5)

```

####Question 7####
```{r}
ggplot(data = gapminder, aes(x = lifeExp, colour = country, limit_by = "Asia")) +
  geom_density()

# JD: You have to give ggplot only the data that you would like to graph. 
# Because it is a short piece of code, you contain the filtering in ggplot. 
# You could use the base function subset() or filter() in dplyr.

ggplot(data = subset(gapminder, continent == 'Asia'), aes(x = lifeExp)) + 
  geom_density()

# or

ggplot(data = filter(gapminder, continent == 'Asia'), aes(x = lifeExp)) + 
  geom_density()

```

####Question 8a####

```{r}
mean_df <- 
  gapminder %>%
  group_by(continent) %>%  
  summarize(mean_le = mean(lifeExp))
```

#####I know you reviewed this in class, but now I can't remember 
#####(and apparently I didn't copy it down) how to write the mean line for 8b

####Question 8b####

```{r}
ggplot(data = gapminder, aes(x = lifeExp, fill = continent)) + 
  geom_density(alpha = 0.5) +
  geom_vline(data = mean_df, aes(xintercept = mean_le)) +
  facet_wrap(~ continent)
  
# When you had xintercept = "mean_le" you were getting the error: 
# Error: Discrete value supplied to continuous scale
# This is because you told R that you literally want to plot "mean_le" the 
# 'word', rather than indicating the column name mean_le.

ggplot(data = gapminder, aes(x = lifeExp, fill = continent)) + 
  geom_density(alpha = 0.5) +
  facet_wrap(~ continent)
```

####Part III####
#####I have no idea about this one :(

#####However, I did successfully figure out git and Rmarkdown!

So I think you were originally getting tripped up with reading the hw_gapminder.csv 
file into R. You can go and try this out.  

Check what your working directory is:

```{r}
getwd()
```

Hopefully it will be the homework folder that you created at the beginning of the 
class. If not you can set it using:

```{r}
setwd('path to file here')
```

If that's all setup nicely, then you can just run

```{r}
hw_gapminder <- read.csv('./hw_gapminder.csv')

# which is equivalent to:
hw_gapminder <- read.csv('hw_gapminder.csv')
```

If you had a separate place you kept hw_gapminder.csv, say for example, in a 
folder where you store all your data for a certain project called hw_data. You 
can just change the path (the route of folders that you need to traverse to get 
to where you want to be on your computer -- remember this is relative to where 
you're starting, i.e., your working directory). Checkout the read.csv() help 
file for more information.  

Given that, maybe take another stab at trying to find the issues (just for your 
own interest).

```{r, eval = FALSE}

mean_lifeExp <- mean(hw_gapminder$lifeExpe)

small_set <- hw_gapminder[c(1, 2, 3, 4, 1300:1304), ('country', 'continent', 'year')]

mean_gdp <- mean(hw_gapminder$gdpPercap)

max_country <- hw_gapminder$country[which(hw_gapminder$lifeExp = max(hw_gapminder$lifeExp))]

```


